Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-15 krs-survey.tex
Added first pass on KnowRob review + figures for KnowRob and ORO

@@

@@

\subsubsection{Notable experiments}
\label{sect|peis-expe}

@@

\subsubsection{Intrinsic language features}
\label{sect|nkrl-intrinsic-features}

\paragraph{Expressiveness}

\subsubsection{Integration with physical world and in the robot architecture}
\label{sect|nkrl-integration}

>>>>

{\sc KnowRob}~\cite{Tenorth2009a} is an integrated knowledge management system
developed at the Technical University of Munich. It is build as a set of
modules (figure~\ref{fig|knowrob} organized around a core reasoning system
written in Prolog. The core component interfaces through Java/Prolog or
C/Prolog APIs with external modules.

{\sc KnowRob} offers a mechanism called \emph{computables} that allow to
evaluate certain predicates by calling external dedicated functions (for
instance, the valuation of a proposition like \stmt{object1 isOn object2} is
computed when required by calling a specific geometric reasonning module).

\begin{figure}
    \centering
    \includegraphics[scale=0.36]{knowrob.pdf}

    \caption{Overview of the {\sc KnowRob} framework, taken
    from~\cite{Tenorth2011}.}

    \label{fig|knowrob}
\end{figure}

Extension modules plug into the system and provide specialized reasoning
capabilities or interfaces to external data, \eg to read object detections from
the vision system. These modules mainly operate on the level of instances
(ABox).

\paragraph{Knowledge model} {\sc KnowRob} can load OWL ontologies, and the
\emph{KnowRob-Base} ontology is provided as a common-sense ontology, with a
focus on household and kitchen domains. {\sc KnowRob} also store and reason on
introspective knowledge through the \emph{Semantic Robot Description
Language}~\cite{Kunze2011} that allow to represent symbolically the
capabilities of the robot, and is used for planning.

\paragraph{Reasoning Techniques} Amongst the notable {\sc KnowRob} extensions,
{\sc ProbCog}~\cite{Jain2009} is an effort to provide probabilistic reasoning
based on bayesian networks, integration with naive physics reasoning has been
studied~\cite{Kunze2011a}, automatic parsing of Web resource in semi-natural
language has been experimented with~\cite{Tenorth2009b}.

\paragraph{Grounding} Anchoring of knowledge in the {\sc KnowRob} framework
relies on...CoP? Semantic Maps~\cite{Blodow2011}.

%\paragraph{Integration with Decisional Layers} CRAM~\cite{Beetz2010}

\paragraph{Notable Experiments} {\sc KnowRob} has been deployed on several
scenarii at the Technical University of Munich, on the PR2 robot and on a 2-arm
custom mobile manipulator in the scope of the ``assistive
kitchen''~\cite{Beetz2008} project. In these experiments, {\sc KnowRob} has
been used as central knowledge hub...

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.36]{oro.pdf}

    \caption{Overview of the ORO server, taken from~\cite{Lemaignan2012}.}

    \label{fig|oro}
\end{figure}

@@

\paragraph{Notable experiments}
\label{sect|peis-expe}

@@

\paragraph{Intrinsic language features}
\label{sect|nkrl-intrinsic-features}

Expressiveness...

\paragraph{Integration with physical world and in the robot architecture}
\label{sect|nkrl-integration}
